---
title: "A phenologicalOverlap workflow example"
author: "Florian Berger & Carsten F. Dormann"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


# Introduction

The example we had in mind when producing this package was that of a pollinator on a flowering plant: the researcher went out repeatedly, at irregular intervals, and records the presence or abundance of the pollinator species or the flowers of its host. Thus, the typical data are the dates and abundances of two species, for example like this:
```{r make Data, eval=T, echo=T}
A <- cbind.data.frame("doy"=c(41, 42, 45, 55, 56, 57, 62), "abundA"=c(0, 1, 1, 1, 0, 1, 1))
B <- cbind.data.frame("doy"=c(30, 40, 45, 50, 51, 52, 53), "abundB"=c(2, 14, 5, 19, 4, 1, 1))
```
where `doy` refers to day-of-year, starting with the first of January as `1`.
```{r}
hist(rnorm(100), col="green")
```


# Set up the data for analysis

# Decide on whether to fill gaps

# Estimate two PDFs (probability density function) from the data

# Compute the overlap of the two PDFs

# Plotting, error bars, etc


## Original vignette default text:

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
